Text embedding models yield high-resolution insights into conceptual knowledge from short multiple-choice quizzes

### 2024-02-20 paper/main.tex
checkpoint before pulling from jeremymanning/master

As necessary, we then iteratively removed random effects from the maximal model until it successfully converged with a full rank (i.e., non-singular) random effects variance-covariance matrix. 
%When inspecting the model's random effect estimates revealed multiple terms estimated at the boundary of their parameter space (i.e., variance components of 0 or correlation terms of  $\pm 1$), we found that the order in which we eliminated these terms typically did not affect which terms did and did not need to be removed in order for the model to converge to a non-degenerate solution.
When this required eliminating multiple terms whose estimates reached the boundary of their parameter space (i.e., variance components of 0 or correlation terms of  $\pm 1$), we found (qualitatively) that the order in which we did so typically did not affect the set of terms that needed to be removed in order for the model to converge to a non-degenerate solution.
However, in order to ensure consistency in our approach across the 15 separate GLMMs we fit in this set of analyses, we established a general approach to selecting a boundary-estimated parameter to eliminate for each stepwise reduction of the model's complexity, broadly adapted from~\citet{BateEtal15b}.
First, we constrained any correlation terms estimated at the boundary (i.e., $\pm 1$) to 0 and re-fit the model.
This typically resulted in the variance component for the slope or intercept (or possibly both) associated with the zero-constrained correlation being estimated as 0, suggesting which terms we should consider removing.
Second, when choosing which of two variance components to remove from the model, we prioritized removing higher-order terms before removing lower-order terms.
In other words, if the variance components for a random slope and a random intercept were both estimated as 0, we chose to remove the random slope.
Additionally, if constraining a correlation term to 0 allowed the model to converge with a full rank variance-covariance matrix, we left the correlation term constrained rather than removing the associated slope and/or intercept component.
Third, to choose which of two zero-estimated variance components of the \textit{same} order to remove from the model, we took one of two approaches.
If the two components were both random slopes, performed a Principal Components Analysis (PCA) on the random effects variance-covariance matrix, and compared the proportion of variance explained by the second component from each of the two random effect groupings. 
If one If one explains a substantially smaller proportion of variance than the other, we dropped its corresponding random slope.
Alternatively, if the difference in variance explained by the two is (qualitatively) small, or if the two variance components we wanted to choose between were random intercepts rather than slopes, we removed the one whose absence resulted in the greater decrease in the Akaike information criterion (AIC).

>>>>

As necessary, we then iteratively removed random effects from the maximal model until it successfully converged with a full rank (i.e., non-singular) random effects variance-covariance matrix. 
%When inspecting the model's random effect estimates revealed multiple terms estimated at the boundary of their parameter space (i.e., variance components of 0 or correlation terms of  $\pm 1$), we found that the order in which we eliminated these terms typically did not affect which terms did and did not need to be removed in order for the model to converge to a non-degenerate solution.
When this required eliminating multiple terms whose estimates reached the boundary of their parameter space (i.e., variance components of 0 or correlation terms of  $\pm 1$), we found (qualitatively) that the order in which we did so typically did not affect the set of terms that needed to be removed in order for the model to converge to a non-degenerate solution.
However, in order to ensure consistency in our approach across the 15 separate GLMMs we fit in this set of analyses, we established a general approach to selecting a boundary-estimated parameter to eliminate for each stepwise reduction of the model's complexity, broadly adapted from~\citet{BateEtal15b}.
First, we constrained any correlation terms estimated at the boundary (i.e., $\pm 1$) to 0 and re-fit the model.
This typically resulted in the variance component for the slope or intercept (or possibly both) associated with the zero-constrained correlation being estimated as 0, suggesting which terms we should consider removing.
Second, when choosing which of two variance components to remove from the model, we prioritized removing higher-order terms before removing lower-order terms.
In other words, if the variance components for a random slope and a random intercept were both estimated as 0, we chose to remove the random slope.
Additionally, if constraining a correlation term to 0 allowed the model to converge with a full rank variance-covariance matrix, we left the correlation term constrained rather than removing the associated slope and/or intercept component.
Third, to choose which of two zero-estimated variance components of the \textit{same} order to remove from the model, we took one of two approaches.
If the two components were both random slopes, performed a Principal Components Analysis (PCA) on the random effects variance-covariance matrix, and compared the proportion of variance explained by the second component from each of the two random effect groupings. 
If one If one explains a substantially smaller proportion of variance than the other, we dropped its corresponding random slope.
Alternatively, if the difference in variance explained by the two is (qualitatively) small, or if the two variance components we wanted to choose between were random intercepts rather than slopes, we removed the one whose absence resulted in the greater decrease in the Akaike information criterion (AIC).
Finally, once we identify the maximal random effects structure for which the data can yield a full rank variance-covariance matrix, we take no additional steps to further reduce the model's complexity. 
We chose this stopping criterion to roughly approximate a ``middle ground'' between approaches to model specification and selection that emphasize maximalism at the cost of potential singular fits~\citep[e.g.,~][]{BarrEtal13}, and those that emphasize parsimony at the cost of potentially increased Type I error rates~\citep[e.g.,~][]{BateEtal15b}.

To assess the predictive value of these

Next, in order to assess the predictive value of the knowledge estimates

In order to assess the predictive value of the knowledge estimates we used to fit each GLMM, we then fit a \textit{second} model to the same data as each of the 15

In order to assess whether the knowledge estimates we used to fit each GLMM could reliably predict participants' success on held-out questions, we then fit a second GLMM to the observations
